A Large-Scale Study of the Use of Eval in R

### 2020-08-28 inst/paper/main.tex
even more patterns

  \subsubsection{Convenience}
  evaling recorded calls in model-fitting functions or passing most of the
  current call to another function. Both ``patterns'' use the \c{match.call} to
  capture current call. The latter is just for laziness as it is the same as
  calling the new function with explicitly selecting the arguments.

@@

  \subsubsection{Miscellaneous} \eval is also used in R packages to get around
  various limitations. For example, in \datatable package, \eval is used to
  modify a binding in the \base package of R. Bindings in the \base package are
  locked for modification and require explicit unlocking using \unlockBinding
  function. However, directly using this function triggers a
  restricted-function-use warning during package build, preventing the package
  to be accepted by CRAN. The \datatable gets around this limitation by
  enclosing the call to \unlockBinding inside \eval. From the same reason, other
  packages use \eval to access private variables and functions from their
  dependencies.
  % \AllValueInputEvalCallPerc migth hit on a wong usage

>>>>

  \subsubsection{Convenience} Eval is used to make some programming tasks easier (and/or shorter). For example, in \c{data.table}, it is used to set R options from a character vector
  \begin{lstlisting}
opts = c("datatable.verbose"="FALSE", ...)
for (i in names(opts)) eval(parse(text=paste0("options(",i,"=",opts[i],")")))

  \end{lstlisting}
  %
  instead of manually calling \c{options(datatable.verbose=FALSE)}

@@

  \subsubsection{Miscellaneous} \eval is also used in R packages to get around
  various limitations. For example, in \datatable package, \eval is used to
  modify a binding in the \base package of R. Bindings in the \base package are
  locked for modification and require explicit unlocking using \unlockBinding
  function. However, directly using this function triggers a
  restricted-function-use warning during package build, preventing the package
  to be accepted by CRAN. The \datatable gets around this limitation by
  enclosing the call to \unlockBinding inside \eval. From the same reason, other
  packages use \eval to access private variables and functions from their
  dependencies.

  \subsubsection{Unnecessary use of eval} Similarly to JavaScript, there are also unnecessary uses of \eval.
  For example, the \c{PerfromanceAnalytics} package contains a function \c{chart.QQPlot} that uses \eval to resolve a string into function and anther to call it and assign its results into a variable:
  \begin{lstlisting}
function (R, d="norm", dp, ...) {
q.f <- eval(parse(text=paste("q",d,sep="")))
z <- NULL
eval(parse(text=paste("z<-q.f(",dp,",...)")))
}
  \end{lstlisting}
  In both cases, there is no need for \eval:
  \begin{lstlisting}
function (R, d="norm", dp, ...) {
q.f <- get(paste0("q",d))
z <- q.f(dp, ...)
}
  \end{lstlisting}
  or even to a oneliner \c{do.call(paste0("q",d), as.list(dp, ...))}.
